---
title: "Cumulative"
author: "Inam Khan"
format: html
execute: 
  echo: false
  message : false
  warning: false
---

```{r}
library(tidyverse)
library(primer.data)
library(broom)
library(MASS)
```

```{r}
x <- ces |>
  filter(year == 2020) |>
  select(approval, education, ideology) |>
  drop_na() |>
  slice_sample(n = 2000)
```

```{r}
x |>
  ggplot(aes(x = ideology, fill = approval)) +
  geom_bar() +
  labs(
    title = "Relationship Between President Approval and Political Ideology",
    subtitle = "Most respondents, especially liberals, strongly disapprove of the president",
    x = "Political Ideology",
    y = "Count",
    fill = "Approval of the President",
    caption = "Data from CES."
  )
```

Public opinion about political leaders often varies widely across different ideological groups.
Using data from the 2020 Cooperative Election Study (CES), which includes responses from thousands of U.S. adults, we explore how political ideology relates to approval of the president.

However, because many CES respondents are part of the YouGov panel, they may not fully represent the broader U.S. population.


$$
P(Y \leq k) = \frac{1}{1 + \exp\left( -\left( \alpha_k - \beta_1 \cdot \text{ideology} - \beta_2 \cdot \text{education} \right) \right)}
$$

$$
Y \sim \text{Ordinal}(\boldsymbol{\rho}) \quad \text{where} \quad \boldsymbol{\rho} = (\rho_1, \rho_2, \ldots, \rho_K)
$$

